### 2018-03-20 proposal/proposal.tex
Added proposal base tex file

\documentclass[12pt,a4paper]{article}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{amsmath}
\usepackage{enumitem}

\newcommand{\scomment}[1]{{\bf{\color{red}{{[Suyash: #1]}}}}}
\newcommand{\acomment}[1]{{\bf{\color{blue}{{[Aman: #1]}}}}}
\newcommand{\fullref}[1]{\hyperref[{#1}]{\autoref*{#1} - \nameref*{#1}}} % One single link
\newcommand{\figref}[1]{\hyperref[{#1}]{\autoref*{#1}}} % One single link

\hypersetup{
colorlinks=true,
allcolors=blue,
}

\usepackage{geometry}
\geometry{
a4paper,
left=20mm,
top=30mm,
}

\title{COL772: Project Proposal}
\author{Suyash Agrawal (2015CS10262) \\ Aman Agrawal (2015CS10210)}

\begin{document}
\maketitle
\section{Text Classification}
    \bibliographystyle{unsrt}
    \bibliography{proposal}
\end{document}

### 2018-03-20 proposal/proposal.tex
Added basic structure of proposal
Added evaluation section in proposal

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[10pt,a4paper]{article}
 \usepackage{listings}
@@
 \maketitle
-\section{Text Classification}
+\section{Goal}
+    Our aim is to create a model that can learn to auto reply to tweets.
+\section{Dataset}
+\section{Literature}
+    Recently, google released a paper ``Smart Reply''\cite{paper:smartReply}, which is their model for 
+    email auto responder. Apart from this, there are various papers on summarization\cite{paper:pointer}
+    where we plan to take inspiration from.\\
+    We have not found a paper that exactly does twitter replies and thus we would be writing code from scratch.
+\section{Evaluation}
+    For quantitative evaluation, we are currently planning on using the perplexity as our loss measure. The gold
+    labels, would be a held out test data from the whole dataset. We would also be reporting the BLEU, METEOR and
+    ROGUE metric, of our predictions.\\
+    For qualitative evaluation, we can just look at some randomly sampled results and judge their quality.
+
     \bibliographystyle{unsrt}

### 2018-03-20 proposal/proposal.tex
Changed introduction a bit

--- 2018-03-20 proposal/proposal.tex
@@
 \maketitle
-\section{Text Classification}
+\section{Goal}
+    Our aim is to create a model that can learn to generate reply for tweets. Further, we would also experiment
+    with other domains like email and dialogues.
+\section{Dataset}
+\section{Literature}
+    Recently, google released a paper ``Smart Reply''\cite{paper:smartReply}, which is their model for 
+    email auto responder. Apart from this, there are various papers on text summarization\cite{paper:pointer}
+    where we plan to take inspiration from.\\
+    We have not found a paper that exactly does twitter replies and thus we would be writing code from scratch.
+\section{Evaluation}
+    For quantitative evaluation, we are currently planning on using the perplexity as our loss measure. The gold
+    labels, would be a held out test data from the whole dataset. We would also be reporting the BLEU, METEOR and
+    ROGUE metric of our predictions.\\
+    For qualitative evaluation, we can just look at some randomly sampled results and judge their quality.
+
     \bibliographystyle{unsrt}

### 2018-03-20 proposal/proposal.tex
added data section in project proposal

@@
 a4paper,
-left=20mm,
-top=30mm,
+left=19mm,
+right=19mm,
+top=20mm,
 }
@@
     with other domains like email and dialogues.
+
 \section{Dataset}
+We plan to use the Marsan Ma’s curated twitter corpus of $800,000$ context-responses\cite{data:twitter-marson} for our baseline model testing.
+Later, we can actually use the twitter streaming API to mine tweets and their corresponding replies to create our own dataset in a day or so.\\
+We can later extend the dataset by merging it with the Enron Email Dataset, which contains about $500k$ emails of $150$ employees of Enron Corporation\cite{data:enron}. \\
+If, time permits, we can concatenate the Cornell Movie-Dialogs corpus \cite{data:cornell-movie} in addition to the Twitter corpus to train a better model.
+
 \section{Literature}

### 2018-03-20 proposal/proposal.tex
Added final proposal submission

@@
 We plan to use the Marsan Ma’s curated twitter corpus of $800,000$ context-responses\cite{data:twitter-marson} for our baseline model testing.
-Later, we can actually use the twitter streaming API to mine tweets and their corresponding replies to create our own dataset in a day or so.\\
+Later, we can use the twitter streaming API to mine tweets and their corresponding replies to create our own dataset in a day or so.\\
 We can later extend the dataset by merging it with the Enron Email Dataset, which contains about $500k$ emails of $150$ employees of Enron Corporation\cite{data:enron}. \\

### 2018-05-10 paper/acl17-latex/paper.tex
Added paper tex

%
% File acl2017.tex
%
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Automated Essay Scoring}

\author{Aman Agrawal \\
  IIT Delhi \\
  {\tt cs1150210@iitd.ac.in} \\\And
  Suyash Agrawal \\
  IIT Delhi \\
  {\tt cs1150262@iitd.ac.in} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of ACL-2017. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL
and NAACL proceedings, including those for ACL 2017 by Dan Gildea and
Min-Yen Kan, NAACL-2017 by Margaret Mitchell, ACL-2012 by Maggie Li
and Michael White, those from ACL-2010 by Jing-Shing Chang and Philipp
Koehn, those for ACL-2008 by Johanna D. Moore, Simone Teufel, James
Allan, and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal
Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and
earlier ACL and EACL formats. Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted
to ACL-2017 or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The ACL 2017 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

\subsection{The Ruler}
The ACL 2017 style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references ({\em e.g.}, the first paragraph on this page ends at mark $114.5$).

\subsection{Electronically-available resources}

ACL provides this description in \LaTeX2e{} ({\small\tt acl2017.tex}) and PDF
format ({\small\tt acl2017.pdf}), along with the \LaTeX2e{} style file used to
format it ({\small\tt acl2017.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
and example bibliography ({\small\tt acl2017.bib}).
These files are all available at
{\small\tt acl2017.org/index.php?article\_id=9}. We
strongly recommend the use of these style files, which have been
appropriately tailored for the ACL 2017 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using 
{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of 
 your electronic submission, please contact the publication chairs 
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 11 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

{\bf Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document. Do not include page numbers.

{\bf Indent}: When starting a new paragraph. Use 11 points for text and 
subsection headings, 12 points for section headings and 15 points for
the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf  Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals. Do not number subsubsections.

\begin{table*}
\centering
\begin{tabular}{lll}
  output & natbib & previous ACL style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous ACL style files
  for compatibility.
  }
\end{table*}

{\bf Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.
Using the provided \LaTeX\ style, the former is accomplished using
{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.  Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}.  
Append lowercase letters to the year in cases of ambiguities.  
 Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents.

\penalty -5000

We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option:
\verb|\usepackage[nohyperref]{acl2017}|

\textbf{Digital Object Identifiers}:  As part of our work to make ACL
materials more widely used and cited outside of our discipline, ACL
has registered as a CrossRef member, as a registrant of Digital Object
Identifiers (DOIs), the standard for registering permanent URNs for
referencing scholarly materials.  As of 2017, we are requiring all
camera-ready references to contain the appropriate DOIs (or as a
second resort, the hyperlinked ACL Anthology Identifier) to all cited
works.  Thus, please ensure that you use Bib\TeX records that contain
DOI or URLs for any of the ACL materials that you reference.
Appropriate records should be found for most materials in the current
ACL Anthology at \url{http://aclanthology.info/}.

As examples, we cite \cite{P16-1001} to show you how papers with a DOI
will appear in the bibliography.  We cite \cite{C14-1001} to show how
papers without a DOI but with an ACL Anthology Identifier will appear
in the bibliography.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, {\em e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

\textbf{Please do not use anonymous citations} and do not include
acknowledgements when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM 
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
points text. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 11 point text.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate the color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions.
Here we give a simple criterion on your colored figures, if your paper has to be printed in black and white, then you must assure that every curves or points in your figures can be still clearly distinguished.

% Min: no longer used as of ACL 2017, following ACL exec's decision to
% remove this extra workflow that was not executed much.
% BEGIN: remove
%% \section{XML conversion and supported \LaTeX\ packages}

%% Following ACL 2014 we will also we will attempt to automatically convert 
%% your \LaTeX\ source files to publish papers in machine-readable 
%% XML with semantic markup in the ACL Anthology, in addition to the 
%% traditional PDF format.  This will allow us to create, over the next 
%% few years, a growing corpus of scientific text for our own future research, 
%% and picks up on recent initiatives on converting ACL papers from earlier 
%% years to XML.

%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
%% with the camera-ready version of your paper. We will then convert them
%% to XML automatically, using the LaTeXML tool
%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
%% a number of \LaTeX\ packages, including the ACL 2017 stylefile. These
%% bindings allow LaTeXML to render the commands from these packages
%% correctly in XML. For best results, we encourage you to use the
%% packages that are officially supported by LaTeXML, listed at
%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
% END: remove

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

The ACL 2017 main conference accepts submissions of long papers and
short papers.
 Long papers may consist of up to eight (8) pages of
content plus unlimited pages for references. Upon acceptance, final
versions of long papers will be given one additional page -- up to nine (9)
pages of content plus unlimited pages for references -- so that reviewers' comments
can be taken into account. Short papers may consist of up to four (4)
pages of content, plus unlimited pages for references. Upon
acceptance, short papers will be given five (5) pages in the
proceedings and unlimited pages for references.

For both long and short papers, all illustrations and tables that are part
of the main text must be accommodated within these page limits, observing
the formatting instructions given in the present document. Supplementary
material in the form of appendices does not count towards the page limit.

However, note that supplementary material should be supplementary
(rather than central) to the paper, and that reviewers may ignore
supplementary material when reviewing the paper (see Appendix
\ref{sec:supplemental}). Papers that do not conform to the specified
length and formatting requirements are subject to be rejected without
review.

Workshop chairs may have different rules for allowed length and
whether supplemental material is welcome. As always, the respective
call for papers is the authoritative source.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review.

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2017}
\bibliography{acl2017}
\bibliographystyle{acl_natbib}

\appendix

\section{Supplemental Material}
\label{sec:supplemental}
ACL 2017 also encourages the submission of supplementary material
to report preprocessing decisions, model parameters, and other details
necessary for the replication of the experiments reported in the 
paper. Seemingly small preprocessing decisions can sometimes make
a large difference in performance, so it is crucial to record such
decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather
than central) to the paper. {\bf Submissions that misuse the supplementary 
material may be rejected without review.}
Essentially, supplementary material may include explanations or details
of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system,
pseudo-code or source code, and data. (Source code and data should
be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper
may refer to and cite the supplementary material and the supplementary material will be available to the
reviewers, they will not be asked to review the
supplementary material.

Appendices ({\em i.e.} supplementary material in the form of proofs, tables,
or pseudo-code) should come after the references, as shown here. Use
\verb|\appendix| before any appendix section to switch the section
numbering over to letters.

\section{Multiple Appendices}
\dots can be gotten by using more than one section. We hope you won't
need that.

\end{document}

### 2018-05-10 paper/acl17-latex/paper.tex
Added abstract

@@
 \begin{abstract}
-  This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of ACL-2017. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document.
+  Recent advances in deep learning have produced state of art results in
+  the task of automated essay scoring. The performance of these
+  systems are not tested are approaching human level in the evaluation metrics,
+  but their performance in actual scenarios is not explored. In this paper we explore
+  how well these systems perform in real life scenarios as compared to non-neural
+  models. We also explore some ways to overcome these shortcomings.
 \end{abstract}
 
-\section{Credits}
+\section{Introduction}
 
-This document has been adapted from the instructions for earlier ACL
-and NAACL proceedings, including those for ACL 2017 by Dan Gildea and
-Min-Yen Kan, NAACL-2017 by Margaret Mitchell, ACL-2012 by Maggie Li
-and Michael White, those from ACL-2010 by Jing-Shing Chang and Philipp
-Koehn, those for ACL-2008 by Johanna D. Moore, Simone Teufel, James
-Allan, and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal
-Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and
-earlier ACL and EACL formats. Those versions were written by several
-people, including John Chen, Henry S. Thompson and Donald
-Walker. Additional elements were taken from the formatting
-instructions of the {\em International Joint Conference on Artificial
-  Intelligence} and the \emph{Conference on Computer Vision and
-  Pattern Recognition}.
-
-\section{Introduction}
+There is a recent surge in use of deep learning for the task of automated essay scoring.
+These models have shown to out perform the traditional models based on hand coded features
+and currently have the state of art performance in this task. The current state of art model
+is from Taghipour et al. \cite{nea}
 

### 2018-05-10 paper/acl17-latex/paper.tex
finished abstract

@@
 \begin{abstract}
-  Recent advances in deep learning have produced state of art results in
-  the task of automated essay scoring. The performance of these
-  systems are not tested are approaching human level in the evaluation metrics,
-  but their performance in actual scenarios is not explored. In this paper we explore
-  how well these systems perform in real life scenarios as compared to non-neural
-  models. We also explore some ways to overcome these shortcomings.
+  Automated essay scoring systems are used in evaluating and scoring student essays written based on a given prompt.
+Recent advances in Deep Learning and Natural Language Processing have produced state of art results in this task.
+The performance of these systems are approaching human level according to the evaluation metrics, but their qualitative performance in actual scenarios is not explored.
+In this paper we explore these systems perform in real life scenarios as compared to other non-neural models.
+We also explore some ways to overcome these shortcomings.
 \end{abstract}

### 2018-05-10 paper/acl17-latex/paper.tex
Added new paragraph in introduction

@@
 and currently have the state of art performance in this task. The current state of art model
-is from Taghipour et al. \cite{nea}
+is from Taghipour et al. \cite{nea} and the state of art non-neural model is EASE \cite{ease}.
+In this paper we explore the performance of deep-learning based systems on real life scenarios.
+We try to see if their performance is actually better than traditional non-neural based models in qualitative sense.
+
+Essay writing is usually a part of the student assessment  process.
+Several  organizations,  such  as Educational Testing Service (ETS)\cite{ets}, evaluate the writing skills of students in their examinations.
+Because of the large number of  students participating in these exams, grading all essays is very time-consuming.
+Thus, some organizations have been using AES systems to reduce the time and cost of scoring essays.
+Therefore, it is of prime importance that we understand the metrics that these new models are actually using to score the essays.
 

### 2018-05-10 paper/acl17-latex/paper.tex
Added introduction

@@
 
-The following instructions are directed to authors of papers submitted
-to ACL-2017 or accepted for publication in its proceedings. All
-authors are required to adhere to these specifications. Authors are
-required to provide a Portable Document Format (PDF) version of their
-papers. \textbf{The proceedings are designed for printing on A4
-paper.}
+Automated essay scoring refers to the process of grading student essays without human interference.
+An AES system takes as input an essay written for a given prompt, and then assigns a numeric score to the essay reflecting its quality, based on its  content, grammar, and organization.
+
+Our experiments on the AES systems aims to test the response of models to spelling and grammatical errors.
+It also tests if the model really considers the flow of ideas and organization of essay.
+Along with this, we also try to test if model recoginzes deviation from topic.
+Effect of length of essay is also studied.
+We finally suggest some ways to improve the performance of model on these metrics.
+
+The rest of this paper is organized as follows.
+Section 2 gives an overview of related work in the literature.
+Section 3 describes the  details of our experiments, and present and discuss the results of our experimental evaluation in Section 4.
+Finally, we suggest some ways to improve the models in Section 5 and conclude the paper in Section 6.
 

### 2018-05-10 paper/acl17-latex/paper.tex
added citations

--- 2018-05-10 paper/acl17-latex/paper.tex
@@
 
-There is a recent surge in use of deep learning for the task of automated essay scoring.
-These models have shown to out perform the traditional models based on hand coded features
-and currently have the state of art performance in this task. The current state of art model
-is from Taghipour et al. \cite{nea} and the state of art non-neural model is EASE \cite{ease}.
+Automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
+The performance of these systems is assessed by comparing their scores assigned to a set of essays to human-assigned gold-standard scores.
+Since the output of AES systems is usually a real valued number, the task is often addressed as a supervised machine learning task.
+Recently, there is a lot of development of deep neural models for the task of automated essay scoring.
+These models have shown to out perform the traditional models based on hand coded features and currently have the state of art performance in this task.
+The current state of art model is from Taghipour et al.
+\cite{nea} and the state of art non-neural model is EASE \cite{ease}.
 In this paper we explore the performance of deep-learning based systems on real life scenarios.
@@
 %\bibliography{acl2017}
-\bibliography{acl2017}
+\bibliography{paper}
 \bibliographystyle{acl_natbib}

### 2018-05-11 paper/acl17-latex/paper.tex
added related work

--- 2018-05-10 paper/acl17-latex/paper.tex
@@
 \begin{abstract}
-  Automated essay scoring systems are used in evaluating and scoring student essays written based on a given prompt.
+  Automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
 Recent advances in Deep Learning and Natural Language Processing have produced state of art results in this task.
-The performance of these systems are approaching human level according to the evaluation metrics, but their qualitative performance in actual scenarios is not explored.
-In this paper we explore these systems perform in real life scenarios as compared to other non-neural models.
+These systems are approaching human level performance according to the evaluation metrics, but their qualitative performance in actual scenarios is not yet explored.
+In this paper we explore and analyze how these systems perform in real life scenarios as compared to other non-neural models.
 We also explore some ways to overcome these shortcomings.
@@
 
-Automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
+Essay writing is usually a part of the student assessment  process.
+Several  organizations, such as Educational Testing Service (ETS)\cite{ets}, evaluate the writing skills of students in their examinations.
+Because of the large number of students participating in these exams, grading all essays is very time-consuming.
+Thus, automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
 The performance of these systems is assessed by comparing their scores assigned to a set of essays to human-assigned gold-standard scores.
@@
 Recently, there is a lot of development of deep neural models for the task of automated essay scoring.
-These models have shown to out perform the traditional models based on hand coded features and currently have the state of art performance in this task.
-The current state of art model is from Taghipour et al.
-\cite{nea} and the state of art non-neural model is EASE \cite{ease}.
+These models have shown to out perform the traditional models based on hand crafted features and currently have the state of art performance in this task.
+The current state of art model that we presently know of is from Taghipour et al.
+\cite{nea} and the state of art non-neural model is Enhanced AI Scoring Engine (EASE) \cite{ease}.
 In this paper we explore the performance of deep-learning based systems on real life scenarios.
-We try to see if their performance is actually better than traditional non-neural based models in qualitative sense.
+We try to see if their performance is actually better than traditional non-neural based models in a qualitative sense and analyze the issues that these systems can cause.
 
-Essay writing is usually a part of the student assessment  process.
-Several  organizations,  such  as Educational Testing Service (ETS)\cite{ets}, evaluate the writing skills of students in their examinations.
-Because of the large number of  students participating in these exams, grading all essays is very time-consuming.
-Thus, some organizations have been using AES systems to reduce the time and cost of scoring essays.
-Therefore, it is of prime importance that we understand the metrics that these new models are actually using to score the essays.
+  % Our experiments on the AES systems aims to test the response of models to spelling and grammatical errors.
+It also tests if the model really considers the flow of ideas and organization of essay.
+Along with this, we also try to test if model recoginzes deviation from topic.
+Effect of length of essay is also studied.
+We finally suggest some ways to improve the performance of model on these metrics.
 
-The following instructions are directed to authors of papers submitted
-to ACL-2017 or accepted for publication in its proceedings. All
-authors are required to adhere to these specifications. Authors are
-required to provide a Portable Document Format (PDF) version of their
-papers. \textbf{The proceedings are designed for printing on A4
-paper.}
+  % The rest of this paper is organized as follows.
+Section 2 gives an overview of related work in the literature.
+Section 3 describes the  details of our experiments, and present and discuss the results of our experimental evaluation in Section 4.
+Finally, we suggest some ways to improve the models in Section 5 and conclude the paper in Section 6.
 
-\section{General Instructions}
+\section{Related Work}
+
+There exist many automated essay scoring systems \cite{shermis2013handbook} and some of them are being used in high-stakes assessments.
+E-rater \cite{attali2004automated} and Intelligent Essay Assessor \cite{foltz1999intelligent} are two notable examples of AES systems.
+In 2012, a competition on automated essay scoring called \textit{Automated Student Assessment Prize (ASAP)} was organized by Kaggle and sponsored by the Hewlett Foundation.
+A comprehensive comparison of AES systems was made in the ASAP competition.
+Many AES systems have been developed to date, and most of them have been built with hand-crafted features and supervised machine learning algorithms.
+Researchers have devoted a substantial amount of effort to design effective features for automated essay scoring.
+These features can be as simple as essay length \cite{chen2013automated} or more complicated such as lexical complexity, grammaticality of a text \cite{attali2004automated}, or syntactic features \cite{chen2013automated}.
+Readability features \cite{zesch2015task} have also been proposed in the literature as another source of information.
+Moreover, text coherence has also been exploited to assess the flow of information and argumentation of an essay \cite{chen2013automated}.
+A detailed overview of the features used in AES systems can be found in \cite{zesch2015task}.
+
+Recently due to a lot of surge in deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
+Unlike traditional systems these systems, accepts an essay text as input directly and learns the features automatically from the data.
+A lot of models with varying architectures have been developed in the recent years.
+Some of them use a long short-term memory network (LSTM) \cite{taghipour2016neural}, while others use a convolutional neural networks (CNN) \cite{dong2016automatic} for the effect of automatically learning features.
+Some of them also use an augmented method to learn word embeddings \cite{alikaniotis2016automatic}.
+
+\section{ Instructions}
 

### 2018-05-11 paper/acl17-latex/paper.tex
added experiments of spelling, length and word shuffle

@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage{placeins}
+\usepackage{subcaption}
+\usepackage{cleveref}
+\usepackage{listings}
+\usepackage{graphicx}
+\usepackage{enumitem}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\usepackage{mathtools}
+\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
+
+\newcommand{\acomment}[1]{{\bf{\color{blue}{{[Aman: #1]}}}}}
+\newcommand{\bigo}[1]{\ensuremath{\mathcal{O} (#1)}}
+\newcommand{\fullref}[1]{\hyperref[{#1}]{\autoref*{#1} - \nameref*{#1}}} % One single link
+\newcommand{\figref}[1]{\hyperref[{#1}]{\autoref*{#1}}} % One single link
 
@@
 
-  % Our experiments on the AES systems aims to test the response of models to spelling and grammatical errors.
-It also tests if the model really considers the flow of ideas and organization of essay.
-Along with this, we also try to test if model recoginzes deviation from topic.
-Effect of length of essay is also studied.
-We finally suggest some ways to improve the performance of model on these metrics.
-
   % The rest of this paper is organized as follows.
@@
 
-\section{ Instructions}
+We have tried to analyze these models over various qualitative metrics on which a human scorer would have graded the essays.
+We consider the length of the essay, grammatical and spelling mistakes, and the flow of ideas and organization of essay.
+Along with this, we also try to test if any of these models recognize deviation from the specifed topic.
+We finally suggest some ways to improve the performance of model on these qualitative metrics.
 
-Manuscripts must be in two-column format.  Exceptions to the
-two-column format include the title, authors' names and complete
-addresses, which must be centered at the top of the first page, and
-any full-width figures or tables (see the guidelines in
-Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
-pages directly under the top margin. See the guidelines later
-regarding formatting the first page.  The manuscript should be
-printed single-sided and its length
-should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages are numbered for  initial submission. However, {\bf do not number the pages in the camera-ready version}.
+\section{Model}\label{sec:models}
 
-By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
- document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.
-When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.
+\subsection{Neural Model}
 
-The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
-However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.
-The ACL 2017 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.
+The present state of the art neural model is from \cite{taghipour2016neural}.
+They use a simple a LSTM based model, where the output of each LSTM unit is averaged over time, to get a representation of the essay.
+Finally, they use a linear layer with sigmoid activation which maps its input vector generated by the mean-over-time layer to a scalar value and limits the possible scores to the range of $(0, 1)$.
 
-\subsection{The Ruler}
-The ACL 2017 style defines a printed ruler which should be presented in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document without the provided
-style files, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the {\small\verb|\aclfinalcopy|} command in the document preamble.)
+\subsection{Non-Neural Model}
 
-Reviewers: note that the ruler measurements do not align well with
-lines in the paper -- this turns out to be very difficult to do well
-when the paper contains many figures and equations, and, when done,
-looks ugly. In most cases one would expect that the approximate
-location will be adequate, although you can also use fractional
-references ({\em e.g.}, the first paragraph on this page ends at mark $114.5$).
+The state of the art, open-source non neural model is Enhanced AI Scoring Engine (EASE) \cite{ease}.
+Unlike, the neural model, this model uses a lot of hand-crafted features to learn a vector representation of the input essay.
+These hand-crafted features encode the essay length, spelling mistakes, grammatical correctness and some of content-based features.
+Finally, a Gradient Boosting Regressor is used to predict the score of the essay.
 
-\subsection{Electronically-available resources}
+\section{Experiments}
 
-ACL provides this description in \LaTeX2e{} ({\small\tt acl2017.tex}) and PDF
-format ({\small\tt acl2017.pdf}), along with the \LaTeX2e{} style file used to
-format it ({\small\tt acl2017.sty}) and an ACL bibliography style ({\small\tt acl\_natbib.bst})
-and example bibliography ({\small\tt acl2017.bib}).
-These files are all available at
-{\small\tt acl2017.org/index.php?article\_id=9}. We
-strongly recommend the use of these style files, which have been
-appropriately tailored for the ACL 2017 proceedings.
+\subsection{Setup}
+The dataset that we have used in our experiments is the same dataset used in the ASAP competition run by Kaggle.
+We use quadratic weighted Kappa as a quantitative evaluation metric.
+We trained both the state of the art models described in \cref{sec:models} using the code released by the authors.
+Same hyper-parameters were used as reported in respective papers in order to reproduce the results stated in the papers.
 
-\subsection{Format of Electronic Manuscript}
-\label{sect:pdf}
+The dataset contains essay from eight different prompts.
+Since the test data is not publicly available, the model was trained on 64\% of the data and tested on the remaining 20\%.
+The remaining 16\% was used to tune hyper-parameters and select the best model.
+All of our analysis stated below has been done using the test dataset.
 
-For the production of the electronic manuscript you must use Adobe's
-Portable Document Format (PDF). PDF files are usually produced from
-\LaTeX\ using the \textit{pdflatex} command. If your version of
-\LaTeX\ produces Postscript files, you can convert these into PDF
-using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
-Adobe Distiller to generate PDF.
+\subsection{Effect of Length}
 
-Please make sure that your PDF file includes all the necessary fonts
-(especially tree diagrams, symbols, and fonts with Asian
-characters). When you print or create the PDF file, there is usually
-an option in your printer setup to include none, all or just
-non-standard fonts.  Please make sure that you select the option of
-including ALL the fonts. \textbf{Before sending it, test your PDF by
-  printing it from a computer different from the one where it was
-  created.} Moreover, some word processors may generate very large PDF
-files, where each page is rendered as an image. Such images may
-reproduce poorly. In this case, try alternative ways to obtain the
-PDF. One way on some systems is to install a driver for a postscript
-printer, send your document to the printer specifying ``Output to a
-file'', then convert the file to PDF.
+We tried to analyze the effect of the length of the essay on the prediction of the models.
+Typically, low scoring essays have low scores and this can be seen from \cref{fig:length_plot}.
+Let, $\mu_l$ denote the mean length of the essays in the test set and $\sigma_l$ denote the standard deviation of the lengths.
+We selected essays from each prompt that had length less than $\mu_l - 2\sigma_l$ and appended the same essay till the point where the length of the essay exceeded $\mu_l - 2\sigma_l$.
+The mean score of these essays before and after increasing length were calculated and the percentage increase in the score was calculated.
+\ref{length} shows that the average increase in the predicted score of the essay is $100.58\%$ while for some test sets the increase in the score was close to $235.53\%$.
 
-It is of utmost importance to specify the \textbf{A4 format} (21 cm
-x 29.7 cm) when formatting the paper. When working with
-{\tt dvips}, for instance, one should specify {\tt -t a4}.
-Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
-preamble (directly below the \verb|\usepackage| commands). Then using 
-{\tt dvipdf} and/or {\tt pdflatex} which would make it easier for some.
+\begin{figure*}
+  \centering             
+  \begin{subfigure}[ht]{0.475\textwidth}
+      \centering
+      \includegraphics[width=\textwidth,ext=pdf]{{../../plots/score_vs_len_4_test}.pdf}
+  \end{subfigure}
+  \quad
+  \begin{subfigure}[ht]{0.475\textwidth}
+      \centering
+      \includegraphics[width=\textwidth,ext=pdf]{{../../plots/score_vs_len_8_test}.pdf}
+  \end{subfigure}
+  \caption{Distribution of Length of essay and associated score in the test dataset \label{fig:length_plot}}        
+\end{figure*}
 
-Print-outs of the PDF file on A4 paper should be identical to the
-hardcopy version. If you cannot meet the above requirements about the
-production of your electronic submission, please contact the
-publication chairs as soon as possible.
-
-\subsection{Layout}
-\label{ssec:layout}
-
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted. The exact dimensions for a page on A4
-paper are:
-
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
- If you cannot meet the above requirements about the production of 
- your electronic submission, please contact the publication chairs 
- above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's {\bf Times Roman} font should be
-used. In \LaTeX2e{} this is accomplished by putting
-
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-in the preamble. If Times Roman is unavailable, use {\bf Computer
-  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
-  10\% less dense than Adobe's Times Roman font.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|l|rl|}
-\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-document text & 11 pt  &\\
-captions & 11 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
+\begin{table}[]
+  \centering
+  \resizebox{0.5\textwidth}{!}{%
+  \begin{tabular}{|c|c|c|c|}
   \hline
-\end{tabular}
-\end{center}
-\caption{\label{font-table} Font guide. }
+  \textbf{Prompt} & \textbf{Essays Tested} & \textbf{\%increase (Neural)} & \textbf{\%increase (Non-Neural)} \\ \hline
+  1 & 37 & \textbf{72.785} & \textbf{37.240} \\ \hline
+  2 & 45 & 53.428 & \textbf{33.843} \\ \hline
+  3 & 93 & \textbf{137.284} & \textbf{56.061} \\ \hline
+  4 & 85 & \textbf{235.539} & \textbf{44.515} \\ \hline
+  5 & 70 & \textbf{145.933} & \textbf{78.571} \\ \hline
+  6 & 72 & \textbf{119.254} & 161.905 \\ \hline
+  7 & 53 & 40.181 & \textbf{14.659} \\ \hline
+  8 & 23 & 0.279 & \textbf{4.141} \\ \hline
+  \end{tabular}%
+  }
+\caption{Effect of Length}
+\label{length}
 \end{table}
 
-\subsection{The First Page}
-\label{ssec:first}
+\subsection{Effect of Spelling Mistakes}
+We tried to analyze the effect of the spelling mistakes on the prediction of the models.
+We randomly chose 20\% of the words of the essay and then randomly shuffled the characters of the words to generate words with wrong spellings.
+We had a set of predicted scores for the essays with correct spellings and a new set of predicted scores for essays with wrong spellings.
+We calculated QWK between these two sets of scores.
+\cref{spelling_word} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is very close to 0 for non-neural model.
+Thus, for the neural model there is no disagreement between the scores predicted for essays with correct spellings and essays with 20\% wrong spellings.
 
-Center the title, author's name(s) and affiliation(s) across both
-columns. Do not use footnotes for affiliations. Do not include the
-paper ID number assigned during the submission process. Use the
-two-column format only when you begin the abstract.
+\subsection{Effect of Word Shuffle}
+We tried to analyze the effect of the spelling mistakes on the prediction of the models.
+We randomly shuffled the words of each sentence in the essay.
+This resulted in an essay with terrible grammar, and thus should be scored low by any good AES system.
+We had a set of predicted scores for the essays with good grammar and a new set of predicted scores for essays with bad grammar and a lot of grammatical mistakes.
+We calculated QWK between these two sets of scores.
+\cref{spelling_word} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is significantly less than 1 for the non-neural model.
+Thus, for the neural model there is no disagreement between the scores predicted for essays with correct grammar and essays with bad grammar.
 
-{\bf Title}: Place the title centered at the top of the first page, in
-a 15-point bold font. (For a complete guide to font sizes and styles,
-see Table~\ref{font-table}) Long titles should be typed on two lines
-without a blank line intervening. Approximately, put the title at 2.5
-cm from the top of the page, followed by a blank line, then the
-author's names(s), and the affiliation on the following line. Do not
-use only initials for given names (middle initials are allowed). Do
-not format surnames in all capitals ({\em e.g.}, use ``Mitchell'' not
-``MITCHELL'').  Do not format title and section headings in all
-capitals as well except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.  The affiliation should contain the
-author's complete address, and if possible, an electronic mail
-address. Start the body of the first page 7.5 cm from the top of the
-page.
-
-The title, author names and addresses should be completely identical
-to those entered to the electronical paper submission website in order
-to maintain the consistency of author information among all
-publications of the conference. If they are different, the publication
-chairs may resolve the difference without consulting with you; so it
-is in your own interest to double-check that the information is
-consistent.
-
-{\bf Abstract}: Type the abstract at the beginning of the first
-column. The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by about
-0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
-font above the body of the abstract. The abstract should be a concise
-summary of the general thesis and conclusions of the paper. It should
-be no longer than 200 words. The abstract text should be in 10 point font.
-
-{\bf Text}: Begin typing the main body of the text immediately after
-the abstract, observing the two-column format as shown in 
-the present document. Do not include page numbers.
-
-{\bf Indent}: When starting a new paragraph. Use 11 points for text and 
-subsection headings, 12 points for section headings and 15 points for
-the title.
-
-\begin{table}
+\begin{table*}[h]
   \centering
-\small
-\begin{tabular}{cc}
-\begin{tabular}{|l|l|}
+  \resizebox{\textwidth}{!}{%
+  \begin{tabular}{|c|c|c|c|c|c|}
   \hline
-{\bf Command} & {\bf Output}\\\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular} & 
-\begin{tabular}{|l|l|}
-\hline
-{\bf Command} & {\bf  Output}\\\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\\hline
-\end{tabular}
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, {\em e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
-
-\subsection{Sections}
-
-{\bf Headings}: Type and label section and subsection headings in the
-style shown on the present document.  Use numbered sections (Arabic
-numerals) in order to facilitate cross references. Number subsections
-with the section number and the subsection number separated by a dot,
-in Arabic numerals. Do not number subsubsections.
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-  output & natbib & previous ACL style files\\
-  \hline
-  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
-  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
-  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
-\end{tabular}
-\caption{Citation commands supported by the style file.
-  The citation style is based on the natbib package and
-  supports all natbib citation commands.
-  It also supports commands defined in previous ACL style files
-  for compatibility.
+  \textbf{Prompt} & \textbf{Essays Tested} & \textbf{QWK Spelling (Neural)} & \textbf{QWK Spelling (Non-Neural)} & \textbf{QWK Word Shuffle (Neural)} & \textbf{QWK Word Shuffle (Non- Neural)} \\ \hline
+  1 & 357 & \textbf{0.944} & \textbf{0.027} & \textbf{0.940} & 0.991 \\ \hline
+  2 & 360 & 0.408 & \textbf{0.013} & 0.739 & \textbf{0.515} \\ \hline
+  3 & 345 & \textbf{0.901} & \textbf{0.163} & \textbf{0.893} & 0.709 \\ \hline
+  4 & 355 & \textbf{0.936} & \textbf{0.019} & \textbf{0.930} & \textbf{0.495} \\ \hline
+  5 & 361 & \textbf{0.930} & \textbf{0.027} & \textbf{0.913} & \textbf{0.251} \\ \hline
+  6 & 360 & 0.591 & \textbf{0.017} & \textbf{0.914} & \textbf{0.306} \\ \hline
+  7 & 314 & \textbf{0.871} & \textbf{0.081} & \textbf{0.944} & 0.962 \\ \hline
+  8 & 145 & \textbf{0.822} & \textbf{0.086} & \textbf{0.934} & 0.931 \\ \hline
+  \end{tabular}%
   }
+  \caption{Effect of Spelling Mistakes and Word Shuffle}
+  \label{spelling_word}
   \end{table*}
 
-{\bf Citations}: Citations within the text appear in parentheses
-as~\cite{Gusfield:97} or, if the author's name appears in the text
-itself, as Gusfield~\shortcite{Gusfield:97}.
-Using the provided \LaTeX\ style, the former is accomplished using
-{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.
-Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, {\em e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}.
-Append lowercase letters to the year in cases of ambiguities.  
- Treat double authors as
-in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
-authors are involved. Collapse multiple citations as
-in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
-as sentence constituents.
+\FloatBarrier
 
-\penalty -5000
-
-We suggest that instead of
-\begin{quote}
-  ``\cite{Gusfield:97} showed that ...''
-\end{quote}
-you use
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}   showed that ...''
-\end{quote}
-
-If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
-can use the command \verb|\citet| (cite in text)
-to get ``author (year)'' citations.
-
-If the Bib\TeX{} file contains DOI fields, the paper
-title in the references section will appear as a hyperlink
-to the DOI, using the hyperref \LaTeX{} package.
-To disable the hyperref package, load the style file
-with the \verb|nohyperref| option:
-\verb|\usepackage[nohyperref]{acl2017}|
-
-\textbf{Digital Object Identifiers}:  As part of our work to make ACL
-materials more widely used and cited outside of our discipline, ACL
-has registered as a CrossRef member, as a registrant of Digital Object
-Identifiers (DOIs), the standard for registering permanent URNs for
-referencing scholarly materials.  As of 2017, we are requiring all
-camera-ready references to contain the appropriate DOIs (or as a
-second resort, the hyperlinked ACL Anthology Identifier) to all cited
-works.  Thus, please ensure that you use Bib\TeX records that contain
-DOI or URLs for any of the ACL materials that you reference.
-Appropriate records should be found for most materials in the current
-ACL Anthology at \url{http://aclanthology.info/}.
-
-As examples, we cite \cite{P16-1001} to show you how papers with a DOI
-will appear in the bibliography.  We cite \cite{C14-1001} to show how
-papers without a DOI but with an ACL Anthology Identifier will appear
-in the bibliography.
-
-As reviewing will be double-blind, the submitted version of the papers
-should not include the authors' names and affiliations. Furthermore,
-self-references that reveal the author's identity, {\em e.g.},
-\begin{quote}
-``We previously showed \cite{Gusfield:97} ...''  
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
-previously showed ... ''
-\end{quote}
-
-\textbf{Please do not use anonymous citations} and do not include
-acknowledgements when submitting your papers. Papers that do not
-conform to these requirements may be rejected without review.
-
-\textbf{References}: Gather the full set of references together under
-the heading {\bf References}; place the section before any Appendices,
-unless they contain references. Arrange the references alphabetically
-by first author, rather than by order of occurrence in the text.
-Provide as complete a citation as possible, using a consistent format,
-such as the one for {\em Computational Linguistics\/} or the one in the 
-{\em Publication Manual of the American 
-Psychological Association\/}~\cite{APA:83}.  Use of full names for
-authors rather than initials is preferred.  A list of abbreviations
-for common computer science journals can be found in the ACM 
-{\em Computing Reviews\/}~\cite{ACM:83}.
-
-The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
-American Psychological Association format, allowing regular citations, 
-short citations and multiple citations as described above.
-
-{\bf Appendices}: Appendices, if any, directly follow the text and the
-references (but see above).  Letter them in sequence and provide an
-informative title: {\bf Appendix A. Title of Appendix}.
-
-\subsection{Footnotes}
-
-{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
-points text. They may be numbered or referred to by asterisks or other
-symbols.\footnote{This is how a footnote should appear.} Footnotes
-should be separated from the text by a line.\footnote{Note the line
-separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-{\bf Illustrations}: Place figures, tables, and photographs in the
-paper near where they are first discussed, rather than at the end, if
-possible.  Wide illustrations may run across both columns.  Color
-illustrations are discouraged, unless you have verified that  
-they will be understandable when printed in black ink.
-
-{\bf Captions}: Provide a caption for every illustration; number each one
-sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
-Caption of the Table.''  Type the captions of the figures and 
-tables below the body, using 11 point text.
-
-\subsection{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate the color-blind (as well as those printing
-to paper), grayscale readability for all accepted papers will be
-encouraged.  Color is not forbidden, but authors should ensure that
-tables and figures do not rely solely on color to convey critical
-distinctions.
-Here we give a simple criterion on your colored figures, if your paper has to be printed in black and white, then you must assure that every curves or points in your figures can be still clearly distinguished.
-
-% Min: no longer used as of ACL 2017, following ACL exec's decision to
-% remove this extra workflow that was not executed much.
-% BEGIN: remove
-%% \section{XML conversion and supported \LaTeX\ packages}
-
-%% Following ACL 2014 we will also we will attempt to automatically convert 
-%% your \LaTeX\ source files to publish papers in machine-readable 
-%% XML with semantic markup in the ACL Anthology, in addition to the 
-%% traditional PDF format.  This will allow us to create, over the next 
-%% few years, a growing corpus of scientific text for our own future research, 
-%% and picks up on recent initiatives on converting ACL papers from earlier 
-%% years to XML.
-
-%% We encourage you to submit a ZIP file of your \LaTeX\ sources along
-%% with the camera-ready version of your paper. We will then convert them
-%% to XML automatically, using the LaTeXML tool
-%% (\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
-%% a number of \LaTeX\ packages, including the ACL 2017 stylefile. These
-%% bindings allow LaTeXML to render the commands from these packages
-%% correctly in XML. For best results, we encourage you to use the
-%% packages that are officially supported by LaTeXML, listed at
-%% \url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
-% END: remove
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms
-with appropriate transliterations and/or translations
-since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in
-the order of: original-form transliteration ``translation''.
-
-\section{Length of Submission}
-\label{sec:length}
-
-The ACL 2017 main conference accepts submissions of long papers and
-short papers.
- Long papers may consist of up to eight (8) pages of
-content plus unlimited pages for references. Upon acceptance, final
-versions of long papers will be given one additional page -- up to nine (9)
-pages of content plus unlimited pages for references -- so that reviewers' comments
-can be taken into account. Short papers may consist of up to four (4)
-pages of content, plus unlimited pages for references. Upon
-acceptance, short papers will be given five (5) pages in the
-proceedings and unlimited pages for references.
-
-For both long and short papers, all illustrations and tables that are part
-of the main text must be accommodated within these page limits, observing
-the formatting instructions given in the present document. Supplementary
-material in the form of appendices does not count towards the page limit.
-
-However, note that supplementary material should be supplementary
-(rather than central) to the paper, and that reviewers may ignore
-supplementary material when reviewing the paper (see Appendix
-\ref{sec:supplemental}). Papers that do not conform to the specified
-length and formatting requirements are subject to be rejected without
-review.
-
-Workshop chairs may have different rules for allowed length and
-whether supplemental material is welcome. As always, the respective
-call for papers is the authoritative source.
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references.  Do
-not number the acknowledgments section. Do not include this section
-when submitting your paper for review.
-
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2017}
 \bibliography{paper}
@@
 
-\appendix
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-ACL 2017 also encourages the submission of supplementary material
-to report preprocessing decisions, model parameters, and other details
-necessary for the replication of the experiments reported in the 
-paper. Seemingly small preprocessing decisions can sometimes make
-a large difference in performance, so it is crucial to record such
-decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather
-than central) to the paper. {\bf Submissions that misuse the supplementary 
-material may be rejected without review.}
-Essentially, supplementary material may include explanations or details
-of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system,
-pseudo-code or source code, and data. (Source code and data should
-be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper
-may refer to and cite the supplementary material and the supplementary material will be available to the
-reviewers, they will not be asked to review the
-supplementary material.
-
-Appendices ({\em i.e.} supplementary material in the form of proofs, tables,
-or pseudo-code) should come after the references, as shown here. Use
-\verb|\appendix| before any appendix section to switch the section
-numbering over to letters.
-
-\section{Multiple Appendices}
-\dots can be gotten by using more than one section. We hope you won't
-need that.
-
 \end{document}

### 2018-05-11 paper/acl17-latex/paper.tex
completed experiments part and added structure for leftover part

@@
 
-\section{Model}\label{sec:models}
+\section{Models}\label{sec:models}
 
@@
   \hline
-  \textbf{Prompt} & \textbf{Essays Tested} & \textbf{\%increase (Neural)} & \textbf{\%increase (Non-Neural)} \\ \hline
+  \textbf{Prompt} & \textbf{Essays Tested} & \multicolumn{2}{c|}{\textbf{\% Increase}} \\ \hline
+  \textbf{} & \textbf{} & \textbf{Neural} & \textbf{Non-Neural} \\ \hline
   1 & 37 & \textbf{72.785} & \textbf{37.240} \\ \hline
@@
   4 & 85 & \textbf{235.539} & \textbf{44.515} \\ \hline
-  5 & 70 & \textbf{145.933} & \textbf{78.571} \\ \hline
+  5 & 70 & \textbf{145.933} & 78.571 \\ \hline
   6 & 72 & \textbf{119.254} & 161.905 \\ \hline
@@
 We calculated QWK between these two sets of scores.
-\cref{spelling_word} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is very close to 0 for non-neural model.
+\cref{spell_word_sentence} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is very close to 0 for non-neural model.
 Thus, for the neural model there is no disagreement between the scores predicted for essays with correct spellings and essays with 20\% wrong spellings.
 
+% \begin{table}[]
+%   \centering
+%   \resizebox{0.5\textwidth}{!}{%  
+%   \begin{tabular}{|c|c|c|c|}
+%   \hline
+%   \textbf{Prompt} & \textbf{Essays Tested} & \textbf{QWK (Neural)} & \textbf{QWK (Non-Neural)} \\ \hline
+%   1 & 357 & \textbf{0.944} & \textbf{0.027} \\ \hline
+%   2 & 360 & 0.408 & \textbf{0.013} \\ \hline
+%   3 & 345 & \textbf{0.901} & \textbf{0.163} \\ \hline
+%   4 & 355 & \textbf{0.936} & \textbf{0.019} \\ \hline
+%   5 & 361 & \textbf{0.930} & \textbf{0.027} \\ \hline
+%   6 & 360 & 0.591 & \textbf{0.017} \\ \hline
+%   7 & 314 & \textbf{0.871} & \textbf{0.081} \\ \hline
+%   8 & 145 & \textbf{0.822} & \textbf{0.086} \\ \hline
+%   \end{tabular}
+%   }
+%   \caption{Effect of Spelling Mistakes}
+%   \label{spelling}
+%   \end{table}
+
 \subsection{Effect of Word Shuffle}
-We tried to analyze the effect of the spelling mistakes on the prediction of the models.
+We tried to analyze the effect of the bad grammar on the prediction of the models.
 We randomly shuffled the words of each sentence in the essay.
@@
 We calculated QWK between these two sets of scores.
-\cref{spelling_word} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is significantly less than 1 for the non-neural model.
+\cref{spell_word_sentence} shows that for the neural model, the QWK is close to 1 for most prompts whereas it is significantly less than 1 for the non-neural model.
 Thus, for the neural model there is no disagreement between the scores predicted for essays with correct grammar and essays with bad grammar.
 
-\begin{table*}[h]
+% \begin{table}[]
+%   \centering
+%   \resizebox{0.5\textwidth}{!}{%    
+%   \begin{tabular}{|c|c|c|c|}
+%   \hline
+%   \textbf{Prompt} & \textbf{Essays Tested} & \textbf{QWK (Neural)} & \textbf{QWK (Non- Neural)} \\ \hline
+%   1 & 357 & \textbf{0.940} & 0.991 \\ \hline
+%   2 & 360 & 0.739 & \textbf{0.515} \\ \hline
+%   3 & 345 & \textbf{0.893} & 0.709 \\ \hline
+%   4 & 355 & \textbf{0.930} & \textbf{0.495} \\ \hline
+%   5 & 361 & \textbf{0.913} & \textbf{0.251} \\ \hline
+%   6 & 360 & \textbf{0.914} & \textbf{0.306} \\ \hline
+%   7 & 314 & \textbf{0.944} & 0.962 \\ \hline
+%   8 & 145 & \textbf{0.934} & 0.931 \\ \hline
+%   \end{tabular}
+%   }
+%   \caption{Effect of Word Shuffle}
+%   \label{word_shuffle}
+%   \end{table}
+
+\subsection{Effect of Sentence Shuffle}
+  We tried to analyze the effect of the bad organization and flow of ideas on the prediction of the models.
+We randomly shuffled the sentences of the essay.
+This resulted in an essay with terrible organization and flow of ideas, and thus should be scored low by any good AES system.
+We had a set of predicted scores for the essays with good flow of ideas and a new set of predicted scores for essays with a poor organization.
+We calculated QWK between these two sets of scores.
+\cref{spell_word_sentence} shows that for both the the models, the QWK is close to 1 for most prompts.
+Thus, there is no disagreement between the scores predicted for essays with good organization and flow of ideas and essays without it for both the models.
+
+% \begin{table}[]
+%   \centering
+%   \resizebox{0.5\textwidth}{!}{%
+%   \begin{tabular}{|c|c|c|c|}
+%   \hline
+%   \textbf{Prompt} & \textbf{Essays Tested} & \textbf{QWK (Neural)} & \textbf{QWK (Non- Neural)} \\ \hline
+%   1 & 357 & \textbf{0.919} & \textbf{1.000} \\ \hline
+%   2 & 360 & \textbf{0.847} & \textbf{0.997} \\ \hline
+%   3 & 345 & \textbf{0.906} & \textbf{0.995} \\ \hline
+%   4 & 355 & \textbf{0.944} & \textbf{0.986} \\ \hline
+%   5 & 361 & \textbf{0.903} & \textbf{0.998} \\ \hline
+%   6 & 360 & \textbf{0.907} & \textbf{0.984} \\ \hline
+%   7 & 314 & \textbf{0.977} & \textbf{0.998} \\ \hline
+%   8 & 145 & \textbf{0.991} & \textbf{0.999} \\ \hline
+%   \end{tabular}%
+%   }
+%   \caption{Effect of Sentence Shuffle}
+%   \label{sentence_shuffle}
+%   \end{table}
+
+\begin{table*}[]
   \centering
   \resizebox{\textwidth}{!}{%
-  \begin{tabular}{|c|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|c|}
   \hline
-  \textbf{Prompt} & \textbf{Essays Tested} & \textbf{QWK Spelling (Neural)} & \textbf{QWK Spelling (Non-Neural)} & \textbf{QWK Word Shuffle (Neural)} & \textbf{QWK Word Shuffle (Non- Neural)} \\ \hline
-  1 & 357 & \textbf{0.944} & \textbf{0.027} & \textbf{0.940} & 0.991 \\ \hline
-  2 & 360 & 0.408 & \textbf{0.013} & 0.739 & \textbf{0.515} \\ \hline
-  3 & 345 & \textbf{0.901} & \textbf{0.163} & \textbf{0.893} & 0.709 \\ \hline
-  4 & 355 & \textbf{0.936} & \textbf{0.019} & \textbf{0.930} & \textbf{0.495} \\ \hline
-  5 & 361 & \textbf{0.930} & \textbf{0.027} & \textbf{0.913} & \textbf{0.251} \\ \hline
-  6 & 360 & 0.591 & \textbf{0.017} & \textbf{0.914} & \textbf{0.306} \\ \hline
-  7 & 314 & \textbf{0.871} & \textbf{0.081} & \textbf{0.944} & 0.962 \\ \hline
-  8 & 145 & \textbf{0.822} & \textbf{0.086} & \textbf{0.934} & 0.931 \\ \hline
+  \textbf{Prompt} & \textbf{Essays Tested} & \multicolumn{2}{c|}{\textbf{Spelling Mistakes}} & \multicolumn{2}{c|}{\textbf{Word Shuffle}} & \multicolumn{2}{c|}{\textbf{Sentence Shuffle}} \\ \hline
+  \textbf{} & \textbf{} & \textbf{Neural} & \textbf{Non-Neural} & \textbf{Neural} & \textbf{Non-Neural} & \textbf{Neural} & \textbf{Non-Neural} \\ \hline
+  1 & 357 & \textbf{0.944} & \textbf{0.027} & \textbf{0.940} & 0.991 & \textbf{0.919} & \textbf{1.000} \\ \hline
+  2 & 360 & 0.408 & \textbf{0.013} & 0.739 & \textbf{0.515} & \textbf{0.847} & \textbf{0.997} \\ \hline
+  3 & 345 & \textbf{0.901} & \textbf{0.163} & \textbf{0.893} & 0.709 & \textbf{0.906} & \textbf{0.995} \\ \hline
+  4 & 355 & \textbf{0.936} & \textbf{0.019} & \textbf{0.930} & \textbf{0.495} & \textbf{0.944} & \textbf{0.986} \\ \hline
+  5 & 361 & \textbf{0.930} & \textbf{0.027} & \textbf{0.913} & \textbf{0.251} & \textbf{0.903} & \textbf{0.998} \\ \hline
+  6 & 360 & 0.591 & \textbf{0.017} & \textbf{0.914} & \textbf{0.306} & \textbf{0.907} & \textbf{0.984} \\ \hline
+  7 & 314 & \textbf{0.871} & \textbf{0.081} & \textbf{0.944} & 0.962 & \textbf{0.977} & \textbf{0.998} \\ \hline
+  8 & 145 & \textbf{0.822} & \textbf{0.086} & \textbf{0.934} & 0.931 & \textbf{0.991} & \textbf{0.999} \\ \hline
   \end{tabular}%
   }
-  \caption{Effect of Spelling Mistakes and Word Shuffle}
-  \label{spelling_word}
+  \caption{Effect of spelling mistakes, grammatical errors and poor organization in terms of QWK between old predicted scores and new predicted scores}
+  \label{spell_word_sentence}
   \end{table*}
+
+\section{Methods Proposed}
+
+\subsection{Data Bootstrapping}
+
+\acomment{Write this up}
+
+\subsection{New Tokens}
+
+Presently, the neural model used a special symbol of \textit{\textless UNK \textgreater} for out-of-vocabulary words.
+Thus words which have wrong spelling, were replaced with the embedding of \textit{\textless UNK \textgreater}.
+We added a new symbol \textit{\textless MISSPELL \textgreater}.
+We checked if word has correct spelling using a corpus of 200,000+ words and if it had a wrong spelling, it was replaced with the symbol \textit{\textless MISSPELL \textgreater}.
+
+\acomment{Add table for QWK changes with spelling mistakes on this model.}
+
+\subsection{Hierarchial LSTM}
+
+The current SoTA neural model, used basic LSTM cell to encode the whole essay.
+Typically, an essay has a length of about 500 tokens, and it is very hard for a LSTM to remember this long sequence.
+We proposed using hierarchical LSTM network to mitigate the long history length and to model grammar and coherence better.
+We effectively run a LSTM over the words of each sentence and generate a vector representation of the sentence and then run a LSTM over the representations of the sentences learned in the previous layer to generate a representation of the essay.
+
+\acomment{Add table for QWK changes with word and sentence shuffle mistakes on this model.}
+
+\section{Conclusions}
+
+\acomment{Write this up}
 

### 2018-05-12 paper/acl17-latex/paper.tex
Added some sections

@@
 \subsection{Data Bootstrapping}
+In the current dataset, most of the essays are reasonably good and hence the neural models are not able to learn that longer essays does not necessarily mean better scores.
+Also, it is not able to learn that spelling mistakes should reduce the overall score.
+To overcome this problem we propose to augment the dataset with negative examples like adding longer essays with lower scores (by concatenating low score and small essays multiple times).
 
-\acomment{Write this up}
+% \acomment{Write this up}
 
@@
 We added a new symbol \textit{\textless MISSPELL \textgreater}.
-We checked if word has correct spelling using a corpus of 200,000+ words and if it had a wrong spelling, it was replaced with the symbol \textit{\textless MISSPELL \textgreater}.
+We checked if word has correct spelling using a corpus of 200,000+ words and if it had a wrong spelling, it was replaced with the symbol \textit{\textless MISSPELL \textgreater}.\\
+% We tested this by converting $20\%$ words of each essay to a misspelled word and then calculated score given by our new model and previous model.
+Results are shown in \cref{misp_diff} and suggest that \textless MISSPELL \textgreater helps in assigning low scores to misspelled essays.
 
-\acomment{Add table for QWK changes with spelling mistakes on this model.}
+\begin{table}[]
+  \centering
+  \resizebox{0.5\textwidth}{!}{%
+  \begin{tabular}{|l|l|l|l|}
+  \hline
+  \textbf{Prompt} & \textbf{Previous Score} & \textbf{New Score} & \textbf{\% Decrease} \\ \hline
+  1 & 0.647 & 0.588 & \textbf{26.16} \\ \hline
+  2 & 0.469 & 0.268 & \textbf{10.07} \\ \hline
+  3 & 0.590 & 0.606 & \textbf{43.72} \\ \hline
+  4 & 0.458 & 0.376 & \textbf{36.21} \\ \hline
+  5 & 0.603 & 0.567 & \textbf{33.80} \\ \hline
+  6 & 0.667 & 0.618 & \textbf{25.98} \\ \hline
+  7 & 0.532 & 0.418 & \textbf{25.39} \\ \hline
+  8 & 0.614 & 0.449 & \textbf{11.68} \\ \hline
+  \end{tabular}%
+  }
+  \caption{Scores of new model (with \textless MISSPELL\textgreater token) and old model on essays with $20\%$ misspelled words.}
+  \label{misp_diff}
+  \end{table}
+
+% \acomment{Add table for QWK changes with spelling mistakes on this model.}
 
@@
 We proposed using hierarchical LSTM network to mitigate the long history length and to model grammar and coherence better.
-We effectively run a LSTM over the words of each sentence and generate a vector representation of the sentence and then run a LSTM over the representations of the sentences learned in the previous layer to generate a representation of the essay.
+We effectively run a LSTM over the words of each sentence and generate a vector representation of the sentence and then run a LSTM over the representations of the sentences learned in the previous layer to generate a representation of the essay.\\
+We were not able to get satisfactory results with this approach (shown in \cref{hlstm}).
+One of the possible explanations for this is that the dataset size is too small for hierarchical LSTM to learn the grammar.
+% \acomment{Add table for QWK changes with word and sentence shuffle mistakes on this model.}
 
-\acomment{Add table for QWK changes with word and sentence shuffle mistakes on this model.}
+\begin{table}[]
+  \centering
+  \begin{tabular}{|l|l|l|}
+  \hline
+  \textbf{Prompt} & \textbf{LSTM Score} & \textbf{H-LSTM Score} \\ \hline
+  1 & 0.633 & 0.633 \\ \hline
+  2 & 0.408 & 0.401 \\ \hline
+  3 & 0.603 & 0.604 \\ \hline
+  4 & 0.498 & 0.495 \\ \hline
+  5 & 0.626 & 0.618 \\ \hline
+  6 & 0.719 & 0.701 \\ \hline
+  7 & 0.543 & 0.543 \\ \hline
+  8 & 0.531 & 0.532 \\ \hline
+  \end{tabular}
+  \caption{Effect of sentence shuffle on LSTM and Heirarchical LSTM models}
+  \label{hlstm}
+\end{table}
 

### 2018-05-12 paper/acl17-latex/paper.tex
Added rough conclusion

@@
   \centering
-  \resizebox{0.5\textwidth}{!}{%
-  \begin{tabular}{|l|l|l|l|}
+  % \resizebox{0.5\textwidth}{!}{%
+  \begin{tabular}{|l|l|}
   \hline
-  \textbf{Prompt} & \textbf{Previous Score} & \textbf{New Score} & \textbf{\% Decrease} \\ \hline
-  1 & 0.647 & 0.588 & \textbf{26.16} \\ \hline
-  2 & 0.469 & 0.268 & \textbf{10.07} \\ \hline
-  3 & 0.590 & 0.606 & \textbf{43.72} \\ \hline
-  4 & 0.458 & 0.376 & \textbf{36.21} \\ \hline
-  5 & 0.603 & 0.567 & \textbf{33.80} \\ \hline
-  6 & 0.667 & 0.618 & \textbf{25.98} \\ \hline
-  7 & 0.532 & 0.418 & \textbf{25.39} \\ \hline
-  8 & 0.614 & 0.449 & \textbf{11.68} \\ \hline
-  \end{tabular}%
-  }
-  \caption{Scores of new model (with \textless MISSPELL\textgreater token) and old model on essays with $20\%$ misspelled words.}
+  \textbf{Prompt} & \textbf{QWK} \\ \hline
+  1 & 0.792 \\ \hline
+  2 & 0.277 \\ \hline
+  3 & 0.888 \\ \hline
+  4 & 0.837 \\ \hline
+  5 & 0.907 \\ \hline
+  6 & 0.890 \\ \hline
+  7 & 0.636 \\ \hline
+  8 & 0.242 \\ \hline
+  \end{tabular}
+  % }
+  \caption{Effect of adding \textless MISSPELL\textgreater token (measure as QWK score between old prediction and new prediction)}
   \label{misp_diff}
 \end{table}
+
+% \begin{table}[]
+%   \centering
+%   \resizebox{0.5\textwidth}{!}{%
+%   \begin{tabular}{|l|l|l|l|}
+%   \hline
+%   \textbf{Prompt} & \textbf{Previous Score} & \textbf{New Score} & \textbf{\% Decrease} \\ \hline
+%   1 & 0.647 & 0.588 & \textbf{26.16} \\ \hline
+%   2 & 0.469 & 0.268 & \textbf{10.07} \\ \hline
+%   3 & 0.590 & 0.606 & \textbf{43.72} \\ \hline
+%   4 & 0.458 & 0.376 & \textbf{36.21} \\ \hline
+%   5 & 0.603 & 0.567 & \textbf{33.80} \\ \hline
+%   6 & 0.667 & 0.618 & \textbf{25.98} \\ \hline
+%   7 & 0.532 & 0.418 & \textbf{25.39} \\ \hline
+%   8 & 0.614 & 0.449 & \textbf{11.68} \\ \hline
+%   \end{tabular}%
+%   }
+%   \caption{Scores of new model (with \textless MISSPELL\textgreater token) and old model on essays with $20\%$ misspelled words.}
+%   \label{misp_diff}
+%   \end{table}
 
@@
   \centering
-  \begin{tabular}{|l|l|l|}
+  \begin{tabular}{|l|l|}
   \hline
-  \textbf{Prompt} & \textbf{LSTM Score} & \textbf{H-LSTM Score} \\ \hline
-  1 & 0.633 & 0.633 \\ \hline
-  2 & 0.408 & 0.401 \\ \hline
-  3 & 0.603 & 0.604 \\ \hline
-  4 & 0.498 & 0.495 \\ \hline
-  5 & 0.626 & 0.618 \\ \hline
-  6 & 0.719 & 0.701 \\ \hline
-  7 & 0.543 & 0.543 \\ \hline
-  8 & 0.531 & 0.532 \\ \hline
+  \textbf{Prompt} & \textbf{QWK} \\ \hline
+  1 & 0.962 \\ \hline
+  2 & 0.915 \\ \hline
+  3 & 0.912 \\ \hline
+  4 & 0.966 \\ \hline
+  5 & 0.954 \\ \hline
+  6 & 0.934 \\ \hline
+  7 & 0.976 \\ \hline
+  8 & 0.970 \\ \hline
   \end{tabular}
-  \caption{Effect of sentence shuffle on LSTM and Heirarchical LSTM models}
+  \caption{Effect of sentence shuffle (agreement between LSTM and Heirarchical LSTM using QWK metric)}
   \label{hlstm}
@@
 \section{Conclusions}
+In this paper we have analyzed the behavior of neural model for automated essay scoring on various practical scenarios.
+We performed various experiments for effect of length, grammar, spelling, organization and found that neural models perform subpar in these qualitative metrics even while giving state of art performance on the benchmarks.
+This shows that the problem of automated essay scoring is far from being solved and getting human level performance on benchmarks is not the solution.
+This also shows that the current benchmarks are not sufficient for evaluation and calls for the need of better metrics.
+We have also suggest some solution to problems like length-score inflation, misspelled words.
 

### 2018-05-12 paper/acl17-latex/paper.tex
completed full paper report

@@
 
-\title{Automated Essay Scoring}
+\title{Debunking Neural Essay Scoring}
 
@@
 The mean score of these essays before and after increasing length were calculated and the percentage increase in the score was calculated.
-\ref{length} shows that the average increase in the predicted score of the essay is $100.58\%$ while for some test sets the increase in the score was close to $235.53\%$.
+\cref{length} shows that the average increase in the predicted score of the essay is $100.58\%$ while for some test sets the increase in the score was close to $235.53\%$.
 
@@
 
-% \acomment{Write this up}
-
 \subsection{New Tokens}
@@
 We added a new symbol \textit{\textless MISSPELL \textgreater}.
-We checked if word has correct spelling using a corpus of 200,000+ words and if it had a wrong spelling, it was replaced with the symbol \textit{\textless MISSPELL \textgreater}.\\
-% We tested this by converting $20\%$ words of each essay to a misspelled word and then calculated score given by our new model and previous model.
-Results are shown in \cref{misp_diff} and suggest that \textless MISSPELL \textgreater helps in assigning low scores to misspelled essays.
+We checked if word has correct spelling using a corpus of 200,000+ words and if it had a wrong spelling, it was replaced with the symbol \textit{\textless MISSPELL \textgreater}.
+We analyzed the effects of spelling mistakes on this model, and the results are shown in \cref{misp_diff} and suggest that \textless MISSPELL \textgreater helps in assigning low scores to misspelled essays.
 
@@
   1 & 0.792 \\ \hline
-  2 & 0.277 \\ \hline
+  2 & \textbf{0.277} \\ \hline
   3 & 0.888 \\ \hline
@@
   6 & 0.890 \\ \hline
-  7 & 0.636 \\ \hline
-  8 & 0.242 \\ \hline
+  7 & \textbf{0.636} \\ \hline
+  8 & \textbf{0.242} \\ \hline
   \end{tabular}
@@
 Typically, an essay has a length of about 500 tokens, and it is very hard for a LSTM to remember this long sequence.
-We proposed using hierarchical LSTM network to mitigate the long history length and to model grammar and coherence better.
+We propose using an hierarchical LSTM network to mitigate the long history length and to model grammar and coherence better.
 We effectively run a LSTM over the words of each sentence and generate a vector representation of the sentence and then run a LSTM over the representations of the sentences learned in the previous layer to generate a representation of the essay.\\
@@
   \end{tabular}
-  \caption{Effect of sentence shuffle (agreement between LSTM and Heirarchical LSTM using QWK metric)}
+  \caption{Effect of sentence shuffle (agreement between LSTM and Hierarchical LSTM using QWK metric)}
   \label{hlstm}
@@
 In this paper we have analyzed the behavior of neural model for automated essay scoring on various practical scenarios.
-We performed various experiments for effect of length, grammar, spelling, organization and found that neural models perform subpar in these qualitative metrics even while giving state of art performance on the benchmarks.
+We performed various experiments for effect of length, grammar, spelling, organization and found that neural models perform very poorly in these qualitative metrics even while giving state of art performance on the quantitative benchmarks.
 This shows that the problem of automated essay scoring is far from being solved and getting human level performance on benchmarks is not the solution.
-This also shows that the current benchmarks are not sufficient for evaluation and calls for the need of better metrics.
-We have also suggest some solution to problems like length-score inflation, misspelled words.
-
-\acomment{Write this up}
-
-\FloatBarrier
+This also shows that the current benchmarks are not sufficient for evaluation and thus call for the need of better metrics.
+We have also suggested some solutions to problems like length-score inflation, misspelled words, but still questions whether these systems can be deployed in real life.
 

### 2018-05-12 paper/acl17-latex/paper.tex
Added some minor changes

@@
 
-Recently due to a lot of surge in deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
+Recently due to surge in deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
 Unlike traditional systems these systems, accepts an essay text as input directly and learns the features automatically from the data.
@@
 Let, $\mu_l$ denote the mean length of the essays in the test set and $\sigma_l$ denote the standard deviation of the lengths.
-We selected essays from each prompt that had length less than $\mu_l - 2\sigma_l$ and appended the same essay till the point where the length of the essay exceeded $\mu_l - 2\sigma_l$.
-The mean score of these essays before and after increasing length were calculated and the percentage increase in the score was calculated.
+We selected essays from each prompt that had length less than $\mu_l - 2\sigma_l$ and appended the same essay till the point where the length of the essay exceeded $\mu_l + 2\sigma_l$.
+The mean score of these essays before and after increasing length were calculated and the percentage increase in the score was reported.
 \cref{length} shows that the average increase in the predicted score of the essay is $100.58\%$ while for some test sets the increase in the score was close to $235.53\%$.
@@
 We tried to analyze the effect of the spelling mistakes on the prediction of the models.
-We randomly chose 20\% of the words of the essay and then randomly shuffled the characters of the words to generate words with wrong spellings.
+We randomly chose 20\% of the words of the essay and then did a random shuffle of the characters to generate words with wrong spellings.
 We had a set of predicted scores for the essays with correct spellings and a new set of predicted scores for essays with wrong spellings.
@@
 We tried to analyze the effect of the bad grammar on the prediction of the models.
-We randomly shuffled the words of each sentence in the essay.
+We randomly shuffled the positions of words in each sentence of the essay set.
 This resulted in an essay with terrible grammar, and thus should be scored low by any good AES system.
@@
 This also shows that the current benchmarks are not sufficient for evaluation and thus call for the need of better metrics.
-We have also suggested some solutions to problems like length-score inflation, misspelled words, but still questions whether these systems can be deployed in real life.
+We have also suggested some solutions to problems like length-score correlation, misspelled words which seem to provide some robustness to above problems.
 

### 2018-07-29 paper/acl17-latex/paper.tex
Modified Related Works section

@@
 
-Essay writing is usually a part of the student assessment  process.
+Essay writing is one of the most popular ways to assess the skill of a student.
+Educational Testing Service (ETS)\cite{ets} uses essay scoring to assess the writing skill of students, but due to large number of students participating in these exams, it becomes very time consuming.
+Automated essay scoring systems (AES) aims to automate the process of scoring essays.
+This is usually addressed as a supervised regression problem and the performance is judged by comparing the scores to a manually curated dataset of scored essays.
+Recently, a lot of neural methods were proposed for this task and these have shown to give near human level performance in it.
+They seem to outperform the traditional feature based non-neural models like Enhanced AI Scoring Engine (EASE) \cite{ease}.
+In this paper we explore the performance of deep-learning based systems on real life scenarios.
+We try to see compare their performance to traditional non-neural models in a qualitative sense and analyze the issues caused by them.
+
+% Essay writing is usually a part of the student assessment  process.
 Several  organizations, such as Educational Testing Service (ETS)\cite{ets}, evaluate the writing skills of students in their examinations.
 Because of the large number of students participating in these exams, grading all essays is very time-consuming.
-Thus, automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
+% Thus, automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt.
 The performance of these systems is assessed by comparing their scores assigned to a set of essays to human-assigned gold-standard scores.
-Since the output of AES systems is usually a real valued number, the task is often addressed as a supervised machine learning task.
-Recently, there is a lot of development of deep neural models for the task of automated essay scoring.
-These models have shown to out perform the traditional models based on hand crafted features and currently have the state of art performance in this task.
+% Since the output of AES systems is usually a real valued number, the task is often addressed as a supervised machine learning task.
+% Recently, there is a lot of development of deep neural models for the task of automated essay scoring.
+% These models have shown to out perform the traditional models based on hand crafted features and currently have the state of art performance in this task.
 The current state of art model that we presently know of is from Taghipour et al.
 \cite{nea} and the state of art non-neural model is Enhanced AI Scoring Engine (EASE) \cite{ease}.
-In this paper we explore the performance of deep-learning based systems on real life scenarios.
+% In this paper we explore the performance of deep-learning based systems on real life scenarios.
 We try to see if their performance is actually better than traditional non-neural based models in a qualitative sense and analyze the issues that these systems can cause.
@@
 
-There exist many automated essay scoring systems \cite{shermis2013handbook} and some of them are being used in high-stakes assessments.
-E-rater \cite{attali2004automated} and Intelligent Essay Assessor \cite{foltz1999intelligent} are two notable examples of AES systems.
+Currently, there are a lot of essay scoring systems like E-rater \cite{attali2004automated}. The non-neural essay scorer that we use in our analysis is Enhanced AI Scoring Engine (EASE) \cite{ease}
+by edx, which came 3rd in the kaggle competition named \textit{Automated Student Assessment Prize (ASAP)} sponsored by Hewlett Foundation.\\
+Traditionally, the models used various kinds of hand engineered features like: grammaticality \cite{attali2004automated}, essay length \cite{chen2013automated}, text coherence and organization of ideas\cite{chen2013automated} etc.\\
+
+Recently, due to surge in the area of deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
+These models accept an essay text as input and learn the features automatically.
+Various architectures using LSTMs \cite{taghipour2016neural}, CNNs\cite{dong2016automatic} etc.
+have been proposed for automatically learning the features.
+
+% There exist many automated essay scoring systems \cite{shermis2013handbook} and some of them are being used in high-stakes assessments.
+E-rater \cite{attali2004automated} and E-rater \cite{attali2004automated} are two notable examples of AES systems.
 In 2012, a competition on automated essay scoring called \textit{Automated Student Assessment Prize (ASAP)} was organized by Kaggle and sponsored by the Hewlett Foundation.
@@
 
-Recently due to surge in deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
+% Recently due to surge in deep-learning, a lot of neural models have been proposed which claim to beat the human level performance on evaluation metrics.
 Unlike traditional systems these systems, accepts an essay text as input directly and learns the features automatically from the data.
@@
 \subsection{Non-Neural Model}
-
-The state of the art, open-source non neural model is Enhanced AI Scoring Engine (EASE) \cite{ease}.
-Unlike, the neural model, this model uses a lot of hand-crafted features to learn a vector representation of the input essay.
-These hand-crafted features encode the essay length, spelling mistakes, grammatical correctness and some of content-based features.
-Finally, a Gradient Boosting Regressor is used to predict the score of the essay.
+This model numerous features to create a vector representation of the essay.
+The features are chosen to take essay length, spelling mistakes, grammatical correctness and some of content-based features in account thus giving potential to the model to perform well in scoring task.
 
@@
 This shows that the problem of automated essay scoring is far from being solved and getting human level performance on benchmarks is not the solution.
-This also shows that the current benchmarks are not sufficient for evaluation and thus call for the need of better metrics.
+This also shows that the current benchmarks are not sufficient for evaluation and thus the need of better metrics.
 We have also suggested some solutions to problems like length-score correlation, misspelled words which seem to provide some robustness to above problems.
